draft 1

### 2016-05-27 finalwriteup/draft.rmd

opts_chunk$set(fig.width=8, fig.depth = 5, dpi = 300, warning = FALSE, message = FALSE, echo = FALSE)
getwd()
```

@@

```{r insert_data}
# load function for determining number of required samples for 0.8 power
n.samples = function(data = results.core$diff, type.calc = 'one.sample', alt = 'greater'){
        if(type.calc == 'one.sample'){
                d.calc = abs(mean(data))/sd(data)
                pow_pow = pwr.t.test(n = NULL, d = d.calc , sig.level = 0.05, power = .8, type = c(type.calc), alternative = alt)
                return(ceiling(pow_pow$n))
        }

        if(type.calc == 'two.sample'){
                d.calc = abs(mean(data[[1]]) - mean(data[[2]]))/sqrt(mean(c(var(data[[1]]), var(data[[2]]))))
                pow_pow = pwr.t.test(n = NULL, d = d.calc , sig.level = 0.05, power = .8, type = c(type.calc), alternative = 'two.sided')
                return(ceiling(pow_pow$n))
        }

}

@@

The boosted tre model was first tuned using the caret package to optimise the following parameters [@caret]:

* shrinkage = 0.001
* no trees = 10000
* min terminal node size = 20
* max tree depth = 5

>>>>

opts_chunk$set(fig.width=8, fig.depth = 5, dpi = 300, warning = FALSE, message = FALSE, echo = FALSE)
```

@@

```{r insert_data}
# load function for determining number of required samples for 0.8 power
n.samples = function(data = results.core$diff, type.calc = 'one.sample', alt = 'greater'){
        d.calc = abs(mean(data))/sd(data)
        pow_pow = pwr.t.test(n = NULL, d = d.calc , sig.level = 0.05, power = .8, type = c(type.calc), alternative = alt)
        return(ceiling(pow_pow$n))
}

@@

* Boosted trees first tuned using caret package [@caret]:
* shrinkage = 0.001
* no trees = 10000
* min terminal node size = 20
* max tree depth = 5
